---
output: rmarkdown::github_document
---

# sslsaran

Tools to Work with Certificate Transparency ('CT') Logs and Various 'CT' 'APIs'

## Description

The 'IETF' 'RFC' 6962 (<https://tools.ietf.org/html/rfc6962>) describes an
experimental protocol for publicly logging the existence of 'Transport Layer
Security' ('TLS') certificates as they are issued or observed, in a manner
that allows anyone to audit certificate authority ('CA') activity and notice
the issuance of suspect certificates as well as to audit the certificate logs
themselves. Functions are provided as a wrapper around the log server 'API'.
Tools are also provided to interface with other 'Certificate Transparency' 
'APIs' including 'sslmate' <https://sslmate.com/certspotter/api>,
'Symantec' <https://cryptoreport.websecurity.symantec.com/checker/views/ctsearch.jsp>,
Google, and others.

## What's Inside The Tin

The following functions are implemented:

- `cs_get_cert`:	Get Certificate Object
- `cs_list_certs`:	List Certificates
- `get_entries`:	Retrieve Entries from Log
- `get_sth`:	Retrieve Latest Signed Tree Head
- `parse_x509_attributes`:	Parse X.509/X.500 Attribute Strings into a Named List
- `read_log_list`:	Retrieve Certificate Transparency Log List
- `sym_ct_search`:	Search Certificate Transparency Logs via Symatec CryptoReport
- `tr_log_summary`:	Retrieve Certificate Transparency Log Server Summaries from the Google Transparency Report Project
- `tr_report`:	Query Google's Transparency Repoirt for Certificate Information

## Installation

```{r eval=FALSE}
devtools::install_github("hrbrmstr/sslsaran")
```

```{r message=FALSE, warning=FALSE, error=FALSE, include=FALSE}
options(width=120)
```

## Usage

```{r message=FALSE, warning=FALSE, error=FALSE}
library(sslsaran)
library(tidyverse)

# current verison
packageVersion("sslsaran")

# Get available log servers
ll <- read_log_list()

glimpse(ll$logs)

glimpse(ll$operators)
```

```{r message=FALSE, warning=FALSE, error=FALSE, cache=TRUE}
# How many certs? (we'll use a different list for this since Chrome is picky)
# NOTE: This usually takes a bit of time to run as some CT servers are slow 
moar_logs <- read_log_list("https://www.gstatic.com/ct/log_list/all_logs_list.json")

pull(moar_logs$logs, url) %>% 
  map(get_sth) %>% 
  map_dbl("tree_size") %>% 
  sum(na.rm=TRUE) %>% 
  scales::comma()
```

```{r message=FALSE, warning=FALSE, error=FALSE}
# Pick one from the google list
ctl <- ll$logs$url[2]

# Get picked latest signed tree head
sth <- get_sth(ctl)

# Get the last 30 entries
x <- get_entries(ctl, sth$tree_size-30, sth$tree_size-1)

# Take a look
glimpse(x)

map_chr(x$certificate, ~.x$issuer %||% NA) %>% 
  discard(is.na)

map_chr(x$certificate, ~.x$subject %||% NA) %>% 
  discard(is.na)

map(x$certificate, ~.x$alt_names %||% NA) %>% 
  discard(~is.na(.x[1]))
```